Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100

### 2017-05-03 Inelastic/inelastic_main.tex
version to arxiv
version uploaded to archive
revisited author list and typo fix

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
linenumbers,
longbibliography,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}
%]{article}

@@

\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universität Freiburg, 79104 Freiburg, Germany}}

@@

\author{L.~Baudis}\email[E-mail: ]{lbaudis@physik.uzh.ch}\zurich

@@

\author{L.~B\"utikofer}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

@@

\author{D.~Coderre}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

@@

\author{B.~Kaminsky}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

@@

\author{M.~v.~Sivers}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}

>>>>

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
superscriptaddress,
longbibliography,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}
%]{article}

@@

\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universit\"at Freiburg, 79104 Freiburg, Germany}}

@@

\author{L.~Baudis}\email[E-mail: ]{laura.baudis@uzh.ch}\zurich

@@

\author{L.~B\"utikofer}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg

@@

\author{D.~Coderre}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg

@@

\author{B.~Kaminsky}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg

@@

\author{M.~v.~Sivers}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg

### 2017-05-03 Inelastic/intro.tex
revisited author list and typo fix

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 36.9\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy. 
In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.

>>>>

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 39.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy. 
In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.
